---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sets: Set Operations in R

## Overview

**sets** is an R package that provides a comprehensive set of functions for performing set operations, inspired by Python's `set` methods. This package aims to make set operations in R intuitive and accessible, especially for users familiar with Python. The functions in **sets** leverage the `data.table` and `checkmate` packages to ensure efficient and reliable set operations.

## Installation

You can install the `sets` package directly from GitHub.

```r
# Install devtools if you haven't already
install.packages("devtools")

# Install sets package from GitHub
devtools::install_github("pythonicr/sets")
```

## Getting Started

### Basic Usage

Here are some examples demonstrating how to use the functions provided by the **sets** package.

#### Compute the Difference Between Sets

The `sets_difference` function returns the elements in `x` that are not in the other sets.

```{r}
library(sets)

# Compute the difference between sets
difference <- sets_difference(c(1, 2, 3), c(2, 3, 4))
print(difference)
```

#### Check if Two Sets are Equal

The `sets_equal` function checks if two sets `x` and `y` contain the same elements.

```{r}
# Check if sets are equal
equal <- sets_equal(c(1, 2, 3), c(3, 1, 2))
print(equal)
```

#### Compute the Intersection of Sets

The `sets_intersection` function returns the common elements in all sets.

```{r}
# Compute the intersection of sets
intersection <- sets_intersection(c(1, 2, 3), c(2, 3, 4), c(3, 4, 5))
print(intersection)
```

#### Check if Sets are Disjoint

The `sets_isdisjoint` function checks if two or more sets have no elements in common.

```{r}
# Check if sets are disjoint
disjoint1 <- sets_isdisjoint(c(1, 2, 3), c(4, 5, 6))
disjoint2 <- sets_isdisjoint(c(1, 2, 3), c(3, 4, 5))
print(disjoint1)
print(disjoint2)
```

#### Check if a Set is a Subset of Another Set

The `sets_issubset` function checks if all elements of `x` are in `y`.

```{r}
# Check if a set is a subset
subset <- sets_issubset(c(1, 2), c(1, 2, 3))
print(subset)
```

#### Check if a Set is a Superset of Another Set

The `sets_issuperset` function checks if all elements of `y` are in `x`.

```{r}
# Check if a set is a superset
superset <- sets_issuperset(c(1, 2, 3), c(2, 3))
print(superset)
```

#### Compute the Symmetric Difference Between Sets

The `sets_symmetric_difference` function returns elements in either `x` or `y` but not in both.

```{r}
# Compute the symmetric difference between sets
symmetric_difference <- sets_symmetric_difference(c(1, 2, 3), c(3, 4, 5))
print(symmetric_difference)
```

#### Compute the Union of Sets

The `sets_union` function returns all elements present in any of the sets.

```{r}
# Compute the union of sets
union <- sets_union(c(1, 2, 3), c(3, 4, 5))
print(union)
```

## Contributing

We welcome contributions to the **sets** package. If you have suggestions, bug reports, or want to contribute code, please open an issue or submit a pull request on our GitHub repository.

- [x] isdisjoint
- [x] issubset
- [x] issuperset
- [x] union
- [x] intersection
- [x] difference
- [x] symmetric_difference


## License

**sets** is released under the MIT License. See the LICENSE file in the package's repository for more details.